---
title: "Partner - Brenna"
author: "Brenna"
date: "9/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1.\
**Partner's name and username:** Luping Wang ~ lupingw97\

**Most recent commit:** committed new Rmd file ~ "new file update"\

**Able to knit owner_LupingWang?** Yes, no problems.\

**Git/GitHub Tip**: When I first tried to clone the repo, I accidentaly used the url for the owner_LupingWang file instead of the actual repository url. I was confused at first but I get it now.\

# Understanding Concepts
**1. Explain the difference between Git and Github.**\
Git is a control system and Github allows you to access what you've done with Git.\
**2. Can Git and Github be used independently? Why don't we do so? Describe the advantages and disadvantages.**\
They can be used separately, but they are made to work together. Using GitHub with Git lets you collaborate easily and keep track of your work. The only disadvatge I can think of is that it isn't totally straightforward to learn. Figuring out how to push and pull files is a little confusing at first.\
**3. What is a repository in Git and how can you create a repository in Git (write out the command(s))?**\
A repository is like a directory where you can keep your files.\
Use ***git init*** to initialize a repository in the working directory. Then files can be added using ***git add [file]*** and record file changes using ***git commit -m 'commit caption'***.\

# Coding Exercises
1.Find NAs
```{r}
X = c(47,34,33,65,37,NA,43,NA,11,NA,23,NA)
sum(is.na(X)) #Add up all the NAs
```

2. Modify data
```{r}
age = c(25,30,45,60,12,41)
smoker = c('T','F','T','F','F','F')
weight = c(120,137,0,168,91,142)
example_data = data.frame(age,smoker,weight)
#Replace the third element with 150
weight[3] = 150
print(weight[3])
```

3. Functions
```{r}
#Finds the proportion of NAs in a vector
proportionNAs = function(x) {
  mean(is.na(x)) #Calculates (# NAs / # elements)
}

DevideBySum = function(x) {
   x / sum(x, na.rm = TRUE) #Devide x by the sum of its elements, not including NAs
}
```

4. NAs in two different vectors
```{r}
both_na = function(x,y) {
  n = length(x)
  m = length(y)
  counter = 0
  #Check if lengths are the same
  if(n==m) {
    #If they are, loop through indexes and compare elements
    for(i in 1:n) {
      if(is.na(x[i])==TRUE && is.na(y[i])==TRUE) { #Check if ith elements are NA
        counter = counter + 1 #Add one to the count of mutual NAs
      }
    }
    return(counter)
  }
  else {
    print("Error: vectors must be the same length.")
  }
}
```




